Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-18 doc/GMP2015/s01_introduction.tex

\medskip\noindent
\header{(i) Finding (vertex)-maximal generically rigid subsystems}
Fast, graph-based algorithms exist (pebble-
game~\cite{Jacobs:1997:PG}), for locating all maximal,
\dfn{generically rigid} subsystems (defined formally in Section
\ref{sec:prelim}) \uncited. When the input itself is rigid, these
algorithms do nothing, i.e., compute the identity function.

@@

\medskip\noindent
\header{(ii) Optimal Recursive Decomposition (DR-planning).}
Recursive decomposition of geometric constraint systems has been
formalized \uncited and well-studied \uncited as the \dfn
{Decomposition-Recombination (DR)-planning} problem, defined formally in
Section \ref{sec:prelim}. For the above-
mentioned classes of 2D qusecs, generic rigidity is a combinatorial
property and hence each level of the decomposition should, in
principle, be achievable by a graph-based algorithm as in (1), without
involving geometric information in the constraint system. Since many
such decompositions can exist for a given constraint system, criteria
defining desirable or optimal DR-plans and DR-planning algorithms were
given in \uncited. An \dfn{optimal DR-plan} is one that minimizes
the \dfn{size} (defined formally in Section \ref{sec:prelim}, i.e.,
the maximum number of child subsystems of any parent system.
Being exponential the size, the complexity of solving the parent
constraint system from the solutions of the child systems, is overwhelmingly
dominated by it.

However, for general 2D qusecs that could be overconstrained, even
when restricted to bar-joint systems, the optimal DR-planning problem
was shown to be NP-hard \uncited.

\medskip\noindent
\header{(iii) DR-plans for special classes and with other
criteria.}
For a special class of 2D qusecs, namely \dfn{tree-decomposable}
systems \uncited common in computer aided mechanical design, (which
includes ruler-and-compass and Henneberg-I constructible systems), all
DR-plans turn out to be optimal. This satisfies the so-called \dfn
{Church-Rosser} criterion, leading to highly efficient DR-planning
algorithms. For general 2D qusecs, alternate criteria were suggested
such as \dfn{cluster minimality} requiring parent systems to be
composed of a minimal set of at least 2 rigid proper subsystems (i.e.,
no proper subset forms a rigid system); and \dfn{proper maximality},
requiring child subsystems to be maximal rigid proper subsystems of
the parent system. See Section \ref{sec:prelim} for formal definitions.

While polynomial time algorithms were given \uncited to generate DR-
plans meeting the cluster minimality criterion, no such algorithm is
known for the latter criterion.

\medskip\noindent
\header{(iv) Optimal Recombination and Solution Space Navigation.}
For the entire DR-plan, finding all desired solutions is barely
tractable even if recombination of solved subsystems is easy for each
indecomposable parent system in the DR-plan. This is because even for
the simplest, highly decomposable systems with small DR-plans, the
problem of finding even a single solution to the input system at the
root of the DR-plan is NP-hard \uncited and there is a combinatorial
explosion of solutions \uncited. Typically, however, the desired
solution has a given orientation type, in which case, the crux of the
difficulty is concentrated in the algebraic complexity of
(re)combining child system solutions, to give a solution to the parent
system at any given level of the DR-plan. For fairly general 3D
constraint systems, there are algorithms with formal guarantees that
uncover underlying matroids to combinatorially obtain an optimal
parameterization to minimize the algebraic complexity of the
indecomposable parent (sub)systems that occur in the DR-plan
\uncited\uncited\uncited, provided the DR-plan meets some of the
abovementioned criteria.

However, the generality of these algorithms trades-off against
efficiency, and despite the optimization, the best algorithms can
still take exponential time in the number of child subsystems (which
can be arbitrarily large even for optimal DR-plans) in order to
guarantee all solutions of a given orientation type, even for a single
(sub)system in a DR-plan. They are prohibitively slow in practice. We
note that, utilizing the DR-plan and optimal recombination as a
principled basis, high performance heuristics and software exists
\uncited\uncited to tame combinatorial explosion via user intervention.

\medskip\noindent
\header{(v) Configuration Spaces of Under-constrained Systems.}
For under-constrained 2D bar-joint and body-hyperpin qusecs obtained
from various subclasses of tree-decomposable systems, algorithms have
been developed \uncited\uncited to complete them into isostatic systems
\uncited\uncited and to find paths within the connected components
\uncited\uncited of standard Cartesian configuration spaces. Most of the
algorithms with formal guarantees leverage Cayley configuration space
theory \uncited\uncited to characterize subclasses of graphs and
additional constraints that control combinatorial explosion, and
provide faithful bijective representation of connected components and
paths. These algorithms have decreasing efficiency as the subclass of
systems gets bigger, with highest efficiency for underlying partial
2-tree graphs (alternately called, tree-width 2, series-parallel, $K_4$
minor avoiding), moderate efficiency for 1 degree- of-freedom (dof)
graphs with low Cayley complexity (which include common linkages such
as the Strandbeest, Limacon and Cardioid), and decreased efficiency
for general 1-dof tree-decomposable graphs. While software suites
exist \uncited\uncited, no such formal algorithms and guarantees are known
for non-tree-decomposable systems.
%
\subsection{Contributions and Organization}
\label{sec:cont}

>>>>

\medskip\noindent
\header{(i) Finding (vertex)-maximal generically rigid subsystems}
Fast, graph-based algorithms exist (pebble-game \cite{Jacobs:1997:PG,lee2005finding}), for locating all maximal,
\dfn{generically rigid} subsystems (defined formally in Section
\ref{sec:prelim}). When the input itself is rigid, these
algorithms do nothing, i.e., compute the identity function.

@@

\medskip\noindent
\header{(ii) Optimal Recursive Decomposition (DR-planning).}
Recursive decomposition of geometric constraint systems has been
formalized \cite{hoffman2001decompositionI,hoffman2001decompositionII} and well-studied \cite{jermann2006decomposition,sitharam2005combinatorial} as the 
\dfn {Decomposition-Recombination (DR)-planning} problem, defined formally in
Section \ref{sec:prelim}. For the above-
mentioned classes of 2D qusecs, generic rigidity is a combinatorial
property and hence each level of the decomposition should, in
principle, be achievable by a graph-based algorithm as in (1), without
involving geometric information in the constraint system. Since many
such decompositions can exist for a given constraint system, criteria
defining desirable or optimal DR-plans and DR-planning algorithms were
given in \cite{hoffman2001decompositionI}. An \dfn{optimal DR-plan} is one that minimizes
the \dfn{size} (defined formally in Section \ref{sec:prelim}, i.e.,
the maximum number of child subsystems of any parent system.
Being exponential the size, the complexity of solving the parent
constraint system from the solutions of the child systems, is overwhelmingly
dominated by it.

However, for general 2D qusecs that could be overconstrained, even
when restricted to bar-joint systems, the optimal DR-planning problem
was shown to be NP-hard \cite{lomonosov2004graph}.

\medskip\noindent
\header{(iii) DR-plans for special classes and with other
criteria.}
For a special class of 2D qusecs, namely \dfn{tree-decomposable}
systems  \cite{fudos1997graph,owen1991algebraic,joan-arinyo2004revisiting}  common in computer aided mechanical design, (which
includes ruler-and-compass and Henneberg-I constructible systems), all
DR-plans turn out to be optimal. This satisfies the so-called \dfn
{Church-Rosser} criterion, leading to highly efficient DR-planning
algorithms. For general 2D qusecs, alternate criteria were suggested
such as \dfn{cluster minimality} requiring parent systems to be
composed of a minimal set of at least 2 rigid proper subsystems (i.e.,
no proper subset forms a rigid system); and \dfn{proper maximality},
requiring child subsystems to be maximal rigid proper subsystems of
the parent system. See Section \ref{sec:prelim} for formal definitions.

While polynomial time algorithms were given \cite{hoffman2001decompositionI} to generate DR-
plans meeting the cluster minimality criterion, no such algorithm is
known for the latter criterion.

\medskip\noindent
\header{(iv) Optimal Recombination and Solution Space Navigation.}
For the entire DR-plan, finding all desired solutions is barely
tractable even if recombination of solved subsystems is easy for each
indecomposable parent system in the DR-plan. This is because even for
the simplest, highly decomposable systems with small DR-plans, the
problem of finding even a single solution to the input system at the
root of the DR-plan is NP-hard  \cite{saxe1979embeddability} 
and there is a combinatorial explosion of solutions \cite{borcea2004number}. Typically, however, the desired
solution has a given orientation type, in which case, the crux of the
difficulty is concentrated in the algebraic complexity of
(re)combining child system solutions, to give a solution to the parent
system at any given level of the DR-plan. For fairly general 3D
constraint systems, there are algorithms with formal guarantees that
uncover underlying matroids to combinatorially obtain an optimal
parameterization to minimize the algebraic complexity of the
indecomposable parent (sub)systems that occur in the DR-plan
\cite{sitharam2010optimized,sitharam2006well,sitharam2010reconciling}, provided the DR-plan meets some of the
abovementioned criteria.

However, the generality of these algorithms trades-off against
efficiency, and despite the optimization, the best algorithms can
still take exponential time in the number of child subsystems (which
can be arbitrarily large even for optimal DR-plans) in order to
guarantee all solutions of a given orientation type, even for a single
(sub)system in a DR-plan. They are prohibitively slow in practice. We
note that, utilizing the DR-plan and optimal recombination as a
principled basis, high performance heuristics and software exists
\cite{sitharam2006solution} to tame combinatorial explosion via user intervention.

\medskip\noindent
\header{(v) Configuration Spaces of Under-constrained Systems.}
For under-constrained 2D bar-joint and body-hyperpin qusecs obtained
from various subclasses of tree-decomposable systems, algorithms have
been developed to complete them into isostatic systems
\cite{joan-arinyo2003transforming,sitharam2005combinatorial,gao2006ctree,sitharam2010convex} and to find paths within the connected components
\cite{sitharam2011cayleyI,hidalgo2011reachability} of standard Cartesian configuration spaces. 
Most of the
algorithms with formal guarantees leverage Cayley configuration space
theory \cite{sitharam2010convex,sitharam2011cayleyI,sitharam2011cayleyII} to characterize subclasses of graphs and
additional constraints that control combinatorial explosion, and
provide faithful bijective representation of connected components and
paths. These algorithms have decreasing efficiency as the subclass of
systems gets bigger, with highest efficiency for underlying partial
2-tree graphs (alternately called, tree-width 2, series-parallel, $K_4$
minor avoiding), moderate efficiency for 1 degree- of-freedom (dof)
graphs with low Cayley complexity (which include common linkages such
as the Strandbeest, Limacon and Cardioid), and decreased efficiency
for general 1-dof tree-decomposable graphs. While software suites
exist  \cite{keycurriculum1995geometer,porta2014open,siemens1999d,todd2007geometry}, no such formal algorithms and guarantees are known
for non-tree-decomposable systems.
%
\subsection{Contributions and Organization}
\label{sec:cont}

### 2014-12-18 doc/GMP2015/s02_preliminaries.tex

One important property of generic constraint system or (hyper)graph
%that depends on the appropriate rigidity matrix of indeterminates
is \dfn{rigidity} (\note we refer to these as properties of
the constraint system or as properties of the underlying (hyper)graph
interchangeably), i.e., the realizations or solutions of the
corresponding constraint system being generically isolated and zero-
dimensional.%(if the constraint system has equalities and exact values for the parameters $\delta$).
The result by Asimow and Roth \uncited shows a constraint
(hyper)graph is rigid if it is generically \dfn{infinitesimally
rigid}, i.e.\ the number of independent rows of its appropriate
rigidity matrix is at least the number of columns less the number of
rigid body motions, which is 3 for bar-joint systems.
%This condition is called generic {\em infinitesimal rigidity}.

@@

Defining the combinatorial independence of a subset of edges $E'
\subseteq E$ to be the generic independence of corresponding rows in
the appropriate rigidity matrix of indeterminates, we obtain the
\dfn{rigidity matroid} of a constraint (hyper)graph $G = (V,E)$.%The 2-dimensional {\em rigidity matroid} of a constraint (hyper)graph $G = (V,E)$ is a linear matroid  on $E$,
%where a subset of edges $E' \subseteq E$ is {\em independent} in the matroid,
%if the set of corresponding rows in the appropriate rigidity matrix of indeterminates are linearly independent.
There are various results on combinatorial characterization of
independence and rigidity  and rigidity matroids for different types
of graphs. For bar-joint rigidity matroid, the famous Laman's theorem
\uncited states that the underlying graph is isostatic if and only if
$|E| = 2|V|-3$ and $|E'| \le 2|V'|-3$ for every induced subgraph with
at least 2 vertices. The result by Lovasz and Yemini \uncited  shows
that all 6-vertex-connected graphs are rigid in the plane. For bar-
body rigidity matroid, Tay \uncited proved that the underlying
multigraph is isostatic if and only if it can be decomposed as $3$
edge disjoint spanning trees. White and Whiteley \uncited gave the
same characterization using a different technique to study the
algebraic-geometric conditions of genericity, called pure condition.
Lee, Streinu and Theran \uncited defined the \dfn{$(k,l)$-sparsity
matroid}, where a hypergraph $G$ is called \dfn{$(k,l)$-sparse} if
$|E'| \le k|V'| - l$ for any induced subgraph $(V',E')$ with at least
2 vertices, and \dfn{$(k,l)$-tight} if is $(k,l)$-sparse and $|E| =
k|V| - l$. In general, given a $d$-uniform hypergraph, a
$(k,l)$-sparsity condition is matroidal as long as $l \le dk-1$.

@@

    $G$, \uncited {\sl DRP}$(G)$ (see Figure \ref{fig:c2c3ofk33s}, is defined as a forest that has the

>>>>

One important property of generic constraint system or (hyper)graph
%that depends on the appropriate rigidity matrix of indeterminates
is \dfn{rigidity} (\note we refer to these as properties of
the constraint system or as properties of the underlying (hyper)graph
interchangeably), i.e., the realizations or solutions of the
corresponding constraint system being generically isolated and zero-
dimensional.%(if the constraint system has equalities and exact values for the parameters $\delta$).
The result by Asimow and Roth \cite{asimow1978rigidity}  shows a constraint
(hyper)graph is rigid if it is generically \dfn{infinitesimally
rigid}, i.e.\ the number of independent rows of its appropriate
rigidity matrix is at least the number of columns less the number of
rigid body motions, which is 3 for bar-joint systems.
%This condition is called generic {\em infinitesimal rigidity}.

@@

Defining the combinatorial independence of a subset of edges $E'
\subseteq E$ to be the generic independence of corresponding rows in
the appropriate rigidity matrix of indeterminates, we obtain the
\dfn{rigidity matroid} of a constraint (hyper)graph $G = (V,E)$.%The 2-dimensional {\em rigidity matroid} of a constraint (hyper)graph $G = (V,E)$ is a linear matroid  on $E$,
%where a subset of edges $E' \subseteq E$ is {\em independent} in the matroid,
%if the set of corresponding rows in the appropriate rigidity matrix of indeterminates are linearly independent.
There are various results on combinatorial characterization of
independence and rigidity  and rigidity matroids for different types
of graphs. For bar-joint rigidity matroid, the famous Laman's theorem
\cite{laman1970graphs} states that the underlying graph is isostatic if and only if
$|E| = 2|V|-3$ and $|E'| \le 2|V'|-3$ for every induced subgraph with
at least 2 vertices. The result by Lovasz and Yemini \cite{lovasz1982generic}  shows
that all 6-vertex-connected graphs are rigid in the plane. For bar-
body rigidity matroid, Tay \cite{tay1976rigidity} proved that the underlying
multigraph is isostatic if and only if it can be decomposed as $3$
edge disjoint spanning trees. White and Whiteley \cite{white1987algebraic} gave the
same characterization using a different technique to study the
algebraic-geometric conditions of genericity, called pure condition.
Lee, Streinu and Theran \cite{lee2007graded} defined the \dfn{$(k,l)$-sparsity
matroid}, where a hypergraph $G$ is called \dfn{$(k,l)$-sparse} if
$|E'| \le k|V'| - l$ for any induced subgraph $(V',E')$ with at least
2 vertices, and \dfn{$(k,l)$-tight} if is $(k,l)$-sparse and $|E| =
k|V| - l$. In general, given a $d$-uniform hypergraph, a
$(k,l)$-sparsity condition is matroidal as long as $l \le dk-1$.

@@

    $G$, \cite{hoffman2001decompositionI} {\sl DRP}$(G)$ (see Figure \ref{fig:c2c3ofk33s}, is defined as a forest that has the

### 2014-12-18 doc/GMP2015/s03_drp.tex

\begin{enumerate}
\item
We show that no subset of the children can union to form $C$, thereby requiring all of them be included in an optimal plan.

@@

%%%%%%%%%%%%%%%

\item
If $C_i \cap C_j$ is well-constrained, then, by Remark \ref{lemma:union_intersection}, $C_i \cup C_j$ is also well-constrained. This means that, by Lemma \ref{lemma:wc_intersection_makes_all_wc}, any two children of $C$ will union to $C$ itself. Thus, any two children are potential choices for the optimal DR-plan as they all create equal fan-in (exactly two) at this level.

However, to guarantee that any two are \vemph{solutions} to $OptimalDRP(G)$, it must ensure minimum fan-in for any descendant. Take the set $S_N=\{1,\dots,N\}$, then we call $I=\bigcap_{k\in S_N}{C_k}$ and $R_k=C\setminus C_k$. Suppose we select $i$ and $j$, where $i\neq j$, as the children. Since
% \[C_i=Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i\}}{R_k}\right)\]
% the children of this node will be
% \[Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i,m\}}{R_k}\right)\]
% and
% \[Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i,n\}}{R_k}\right)\]
$C_i=Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i\}}{R_k}\right)$
the children of this node will be
$Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i,m\}}{R_k}\right)$
and
$Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i,n\}}{R_k}\right)$
for arbitrary $m$ and $n$, where $i,j,m,n$ do not equal each other. \todo{Prove these are valid children? Or is this obvious?} This continues for $N-1$ levels total, always with fan-in of two (the minimum possible), at which point every descendant of $C$ is some $Idc(C,I\cup R_k)$ for $k\in S_N$, with every $k$ appearing at least once. Thus, regardless of the choice of $i,j$ and then $m,n$ etc., the DR-plan has fan-in of two for every node for the next $N$ levels, at which point the nodes contain the same subgraphs.
\end{enumerate}
%
This proof then applies to itself recursively to show that the fan-in of the children will also be minimum, thereby making this the optimal DR-plan.
\end{proof}

@@

\begin{lemma}\label{lemma:wc_intersection_is_C}
$C_i\cup C_j$ is well-constrained if and only if $C_i\cup C_j = C$.
\end{lemma}

\begin{proof}
Assume $C_i\cup C_j \neq C$, then we just found a larger proper subgraph and $C_i,C_j$ were not vertex-maximal to begin with.
%
In the reverse direction, we know $C$ is either some non-leaf node (well-constrained by definition of a DR-plan) or $G$ itself (well-constrained by definition of the problem). Thus, $C_i\cup C_j=C$ is well-constrained.
\end{proof}

\begin{lemma}\label{lemma:wc_intersection_makes_all_wc}
If $C_i\cup C_j$ is well-constrained, then $\forall k: C_i\cup C_k$ is well-constrained.
Alternatively, if $C_i\cup C_j=C$, then $\forall k: C_i\cup C_k=C$.
\end{lemma}

\begin{proof}
In appendix (\ref{sec:appendix}).
\end{proof}

\begin{lemma}\label{lemma:uc_intersection_makes_all_uc}
If $C_i\cap C_j$ is trivial, then $\forall k: C_i\cap C_k$ is trivial.
\end{lemma}

\begin{proof}
Assume there is some $k$ such that $C_i\cap C_k$ is not trivial. By Remark \ref{lemma:union_intersection}, $C_i\cap C_k$ must be well-constrained. Then, by Lemma \ref{lemma:wc_intersection_makes_all_wc}, the intersection between any two children must be well-constrained. This means that $C_i\cap C_j$ is well-constrained. Therefore, such a $k$ cannot exist and all intersections are trivial.
\end{proof}

@@

\todo{Explain just second figure now.}
% We now present two examples of non-tree-decomposable graphs that illustrate the the strength and flexibility of the canonical DR-plan.

>>>>

\medskip\noindent
\vemph{Part 1:} We show that no subset of the children can union to form $C$, thereby requiring all of them be included in an optimal plan.

@@

\medskip\noindent
\vemph{Part 2:} If $C_i \cap C_j$ is well-constrained, then, by Remark \ref{lemma:union_intersection}, $C_i \cup C_j$ is also well-constrained. This means that, by Lemma \ref{lemma:wc_intersection_makes_all_wc}, any two children of $C$ will union to $C$ itself. Thus, any two children are potential choices for the optimal DR-plan as they all create equal fan-in (exactly two) at this level.

However, to guarantee that any two are \vemph{solutions} to $OptimalDRP(G)$, it must ensure minimum fan-in for any descendant. Take the set $S_N=\{1,\dots,N\}$, then we call $I=\bigcap_{k\in S_N}{C_k}$ and $R_k=C\setminus C_k$. Suppose we select $i$ and $j$, where $i\neq j$, as the children. Since
% \[C_i=Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i\}}{R_k}\right)\]
% the children of this node will be
% \[Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i,m\}}{R_k}\right)\]
% and
% \[Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i,n\}}{R_k}\right)\]
$C_i=Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i\}}{R_k}\right)$
the children of this node will be
$Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i,m\}}{R_k}\right)$
and
$Idc\left(C,I\cup\bigcup_{k\in S_N\setminus\{i,n\}}{R_k}\right)$
for arbitrary $m$ and $n$, where $i,j,m,n$ do not equal each other. \todo{Prove these are valid children? Or is this obvious?} This continues for $N-1$ levels total, always with fan-in of two (the minimum possible), at which point every descendant of $C$ is some $Idc(C,I\cup R_k)$ for $k\in S_N$, with every $k$ appearing at least once. Thus, regardless of the choice of $i,j$ and then $m,n$ etc., the DR-plan has fan-in of two for every node for the next $N$ levels, at which point the nodes contain the same subgraphs.

This proof then applies to itself recursively to show that the fan-in of the children will also be minimum, thereby making this the optimal DR-plan.
\end{proof}

@@

\begin{lemma}\label{lemma:wc_intersection_is_C}
$C_i\cup C_j$ is well-constrained if and only if $C_i\cup C_j = C$.
\end{lemma}
%
\begin{proof}
Assume $C_i\cup C_j \neq C$, then we just found a larger proper subgraph and $C_i,C_j$ were not vertex-maximal to begin with.
%
In the reverse direction, we know $C$ is either some non-leaf node (well-constrained by definition of a DR-plan) or $G$ itself (well-constrained by definition of the problem). Thus, $C_i\cup C_j=C$ is well-constrained.
\end{proof}
%
%
%
\begin{lemma}\label{lemma:wc_intersection_makes_all_wc}
If $C_i\cup C_j$ is well-constrained, then $\forall k: C_i\cup C_k$ is well-constrained.
Alternatively, if $C_i\cup C_j=C$, then $\forall k: C_i\cup C_k=C$.
\end{lemma}
%
\begin{proof}
In appendix (\ref{sec:appendix}).
\end{proof}
%
%
%
\begin{lemma}\label{lemma:uc_intersection_makes_all_uc}
If $C_i\cap C_j$ is trivial, then $\forall k: C_i\cap C_k$ is trivial.
\end{lemma}
%
\begin{proof}
Assume there is some $k$ such that $C_i\cap C_k$ is not trivial. By Remark \ref{lemma:union_intersection}, $C_i\cap C_k$ must be well-constrained. Then, by Lemma \ref{lemma:wc_intersection_makes_all_wc}, the intersection between any two children must be well-constrained. This means that $C_i\cap C_j$ is well-constrained. Therefore, such a $k$ cannot exist and all intersections are trivial.
\end{proof}

@@

% We now present two examples of non-tree-decomposable graphs that illustrate the the strength and flexibility of the canonical DR-plan.
